Bend or Break? Experimental Evidence of Voters' Punishment for Striking Political Compromises

### 2021-05-06 report/draft.Rmd
add draft

---
title: "Bend or Break? Experimental Evidence of Voters' Punishment for Striking Political Compromises"
date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
output: 
  pdf_document:
    number_sections: true
editor_options: 
  chunk_output_type: console
bibliography: references.bib
urlcolor: blue
linkcolor: blue
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
---
```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
library(knitr)
opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
library(kableExtra)
options(kableExtra.latex.load_packages = FALSE)
library(here)
```

>>>>

---
title: "Bend or Break? Experimental Evidence of Voters' Punishment for Striking Political Compromises"
date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
output: 
  pdf_document:
    number_sections: true
editor_options: 
  chunk_output_type: console
bibliography: references.bib
urlcolor: blue
linkcolor: blue
abstract: "_ADD Abstract_"
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
---
```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
library(knitr)
opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
library(kableExtra)
options(kableExtra.latex.load_packages = FALSE)
library(here)
```
